Manuscript 1 code

### 2025-01-21 manuscript_1_code.Rmd

@@

@@

@@

```{r figure 3a plot}
(figure_3a <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.5) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "", title = "") +
  model_themes 
         )
# ggsave(filename = "output/figure_3a.png", figure_3a, height = 10, width = 14)
```

@@

@@

@@

```{r figure 3b plot}
(figure_3b <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = functional_richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.005) + 
  geom_line(data = filtered_cover_effects_fg, aes(x = functional_richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_fg, aes(x = functional_richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )

#ggsave(filename = "output/figure_3b_quad_v2.png", figure_3b, height = 10, width = 14)
```

@@

### synchrony and cover model

@@

```{r plot figure 3d}
(figure_3d <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_site_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Macroalgal Richness", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_3d.png", figure_3d, height = 10, width = 14)
```

@@

# Figure 4

@@

@@

filtered_rich_stab_effects <- filter_ranges(rich_stab_emm, dss_ranges, "habitat", "richness_mean")
```

@@

# ggsave(filename = "output/figure_4a.png", figure_4a, height = 10, width = 14)
```

@@

@@

filtered_rich_stab_effects_fg <- filter_ranges(rich_stab_emm_fg, dss_ranges, "habitat", "functional_richness_mean")
```

@@

#ggsave(filename = "output/figure_4b_v2.png", figure_4b, height = 10, width = 14)
```

@@

@@

filtered_synch_stab_effects <- filter_ranges(synch_stab_emm, dss_ranges, "habitat", "synchrony")
```

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_stab_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)
```

@@

@@

# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony_stability <- diversity_stability_synchrony %>% 
  dplyr::group_by(habitat, site) %>% 
  dplyr::summarise(synchrony_mean = mean(synchrony, na.rm = T),
            stability_mean = mean(cover_stability, na.rm = T))

>>>>

### mean plot-level alpha diversity metrics

```{r mean plot level adiv}
mean_adiv_quad <- alpha_diversity_quad_macro %>% 
  dplyr::group_by(year, habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness, na.rm = T),
    functional_richness_mean = mean(functional_richness, na.rm = T),
    cover_mean = mean(macroalgal_prop_cover, na.rm = T))

# sv transform cover due to 0s in data
mean_adiv_quad$cover_trans <- sv_trans(mean_adiv_quad$cover_mean)
```

@@

```{r mean richness quad model}
cover_mod_2 <- glmmTMB(cover_trans ~ richness_mean*habitat + (1|site) + (1|year), family = beta_family(), data = mean_adiv_quad)
summary(cover_mod_2)
Anova(cover_mod_2)
#                           Chisq Df Pr(>Chisq)    
# richness_mean         1112.4314  1  < 2.2e-16 ***
# habitat                  4.0269  3     0.2586    
# richness_mean:habitat   25.9539  3  9.752e-06 ***
hist(residuals(cover_mod_2)) # not terrible not great
plot(residuals(cover_mod_2) ~ predict(cover_mod_2)) # heteroskedastic?
performance::r2(cover_mod_2) # 0.774, 0.849
emtrends(cover_mod_2, pairwise ~ habitat, var = "richness_mean") # Fringing different from backreef and FR10, backreef from FR17
# $emtrends
#  habitat      richness_mean.trend     SE  df asymp.LCL asymp.UCL
#  Fringing                    1.77 0.0924 Inf      1.59      1.95
#  Backreef                    1.19 0.0680 Inf      1.06      1.33
#  Forereef 10m                1.44 0.0798 Inf      1.28      1.59
#  Forereef 17m                1.55 0.1020 Inf      1.35      1.75
# 
# $contrasts
#  contrast                    estimate    SE  df z.ratio p.value
#  Fringing - Backreef            0.579 0.116 Inf   4.999  <.0001
#  Fringing - Forereef 10m        0.334 0.120 Inf   2.792  0.0269
#  Fringing - Forereef 17m        0.220 0.132 Inf   1.668  0.3406
#  Backreef - Forereef 10m       -0.245 0.106 Inf  -2.322  0.0929
#  Backreef - Forereef 17m       -0.360 0.124 Inf  -2.896  0.0198
#  Forereef 10m - Forereef 17m   -0.114 0.121 Inf  -0.946  0.7799
```

@@

### V2 SETUP
diversity_ranges_quad_2 <- extract_ranges(mean_adiv_quad, "habitat", c("richness_mean", "cover_trans", "functional_richness_mean"))

cover_emm_2 <- emmip(cover_mod_2,
                   habitat ~ richness_mean,
                   at = list(richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_cover_effects_2 <- filter_ranges(trend = cover_emm_2, range_obj = diversity_ranges_quad_2, group = "habitat", value = "richness_mean")

@@

```{r figure 3a plot}
(figure_3a <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.5) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "", title = "") +
  model_themes 
         )
# ggsave(filename = "output/figure_3a.png", figure_3a, height = 10, width = 14)

## V2
(figure_3a_2 <- 
  ggplot() +
  geom_point(data = mean_adiv_quad,
             aes(x = richness_mean, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects_2, aes(x = richness_mean, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_2, aes(x = richness_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.5) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "", title = "") +
  model_themes 
         )

# ggsave(filename = "output/figure_3a_v2.png", figure_3a_2, height = 10, width = 14)
```

@@

```{r mean fr quad model}

cover_mod_fg_2 <- glmmTMB(cover_trans ~ functional_richness_mean*habitat + (1|site) + (1|year), family = beta_family(), data = mean_adiv_quad)
summary(cover_mod_fg_2)
car::Anova(cover_mod_fg_2)
#                                     Chisq Df Pr(>Chisq)    
# functional_richness_mean         1067.254  1  < 2.2e-16 ***
# habitat                            43.997  3  1.512e-09 ***
# functional_richness_mean:habitat   16.364  3  0.0009549 ***
hist(residuals(cover_mod_fg_2)) # basically the same as the richness mod
plot(residuals(cover_mod_fg_2) ~ predict(cover_mod_fg_2)) # here too

performance::r2(cover_mod_fg_2) # 0.80, 0.84
emtrends(cover_mod_fg_2, pairwise ~ habitat, var = "functional_richness_mean") # fringing different from both FRs
# $emtrends
#  habitat      functional_richness_mean.trend     SE  df asymp.LCL asymp.UCL
#  Fringing                               2.01 0.1070 Inf      1.80      2.22
#  Backreef                               1.81 0.1010 Inf      1.61      2.00
#  Forereef 10m                           1.57 0.0918 Inf      1.39      1.75
#  Forereef 17m                           1.49 0.1040 Inf      1.29      1.69
# $contrasts
#  contrast                    estimate    SE  df z.ratio p.value
#  Fringing - Backreef           0.2035 0.148 Inf   1.374  0.5157
#  Fringing - Forereef 10m       0.4398 0.138 Inf   3.182  0.0080
#  Fringing - Forereef 17m       0.5183 0.142 Inf   3.647  0.0015
#  Backreef - Forereef 10m       0.2363 0.135 Inf   1.752  0.2968
#  Backreef - Forereef 17m       0.3149 0.147 Inf   2.149  0.1378
#  Forereef 10m - Forereef 17m   0.0786 0.131 Inf   0.600  0.9321
```

@@

### V2
cover_emm_fg_2 <- emmip(cover_mod_fg_2,
                        habitat ~ functional_richness_mean,
                        at = list(functional_richness_mean = seq(0,10,0.1)), plotit = F, CIs = T)

filtered_cover_effects_fg_2 <- filter_ranges(cover_emm_fg_2, diversity_ranges_quad_2, "habitat", "functional_richness_mean")
```

@@

```{r figure 3b plot}
(figure_3b <- 
  ggplot() +
  geom_point(data = alpha_diversity_quad_macro,
             aes(x = functional_richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects_fg, aes(x = functional_richness, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_fg, aes(x = functional_richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )
#ggsave(filename = "output/figure_3b_quad_v2.png", figure_3b, height = 10, width = 14)

# V2
(figure_3b_2 <- 
  ggplot() +
  geom_point(data = mean_adiv_quad,
             aes(x = functional_richness_mean, y = cover_trans, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_cover_effects_fg_2, aes(x = functional_richness_mean, y = inv_logit(yvar), colour = habitat)) +
  geom_ribbon(data = filtered_cover_effects_fg_2, aes(x = functional_richness_mean, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )

# ggsave(filename = "output/figure_3b_quad_v3.png", figure_3b_2, height = 10, width = 14)
```

@@

# repeat for the mean of each plot
dss_ranges_2 <- extract_ranges(mean_synchrony_stability, "habitat",
                             c("richness_mean", "functional_richness_mean", "synchrony_mean", "stability_mean", "cover_mean"))
```

### mean plot-level dss setup
```{r mean plot dss}
# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony_stability <- diversity_stability_synchrony %>% 
  dplyr::group_by(habitat, site) %>% 
  dplyr::summarise(
    richness_mean = mean(richness_mean, na.rm = T),
    functional_richness_mean = mean(functional_richness_mean, na.rm = T),
    synchrony_mean = mean(synchrony, na.rm = T),
    stability_mean = mean(cover_stability, na.rm = T),
    cover_mean = mean(cover_mean, na.rm = T))
```
### synchrony and cover model

@@

```{r plot figure 3d}
(figure_3d <- 
  ggplot() +
  geom_point(data = alpha_diversity_site_macro,
             aes(x = richness, y = cover_trans, colour = habitat), size = 1, alpha = 0.3) + 
  geom_line(data = filtered_site_cover_effects, aes(x = richness, y = inv_logit(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_site_cover_effects, aes(x = richness, ymin = inv_logit(LCL), ymax = inv_logit(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Cover\n", x = "Taxonomic Richness", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_3d.png", figure_3d, height = 10, width = 14)
```

@@

### full vs mean plot comparison plot
```{r ggpubr meanfull, fig.height = 8, fig.width=9}

(mean_full_fxn_plot <- ggarrange(figure_3a, figure_3a_2, figure_3b, figure_3b_2, 
                      ncol = 2, nrow = 2, 
                      common.legend = TRUE,
                      legend = "bottom", 
                      font.label = list(size = 26, color = "black", face = "plain")))

# ggsave(filename = "output/figure_3v2.png", figure_3, height = 8, width = 16)
```
```{r figure 3 with mean, fig.height = 8, fig.width=9}
(figure_3_2 <- ggarrange(figure_3a_2, figure_3b_2, figure_3d, figure_3e, 
                      ncol = 2, nrow = 2, 
                      common.legend = TRUE,
                      labels = c("a.", "b.", "c.", "d."),
                      legend = "bottom", 
                      font.label = list(size = 26, color = "black", face = "plain")))

# ggsave(filename = "output/figure_3v3.png", figure_3_2, height = 8, width = 16)

```
# Figure 4

@@

```{r mean plot richstab mod}
rich_stab_mod_2 <- glmmTMB(stability_mean~ richness_mean*habitat , family = Gamma(link = "log"), data = mean_synchrony_stability)
summary(rich_stab_mod_2)
Anova(rich_stab_mod_2)
#                          Chisq Df Pr(>Chisq)    
# richness_mean         213.0187  1  < 2.2e-16 ***
# habitat                29.9628  3  1.405e-06 ***
# richness_mean:habitat   2.8556  3     0.4144    
hist(residuals(rich_stab_mod_2)) #  little chunky
plot(residuals(rich_stab_mod_2) ~ fitted(rich_stab_mod_2)) 
performance::r2(rich_stab_mod_2) # 0.95
emtrends(rich_stab_mod_2, pairwise ~ habitat, var = "richness_mean")  # no differences between sites
# $emtrends
#  habitat      richness_mean.trend     SE  df asymp.LCL asymp.UCL
#  Fringing                   0.796 0.1060 Inf     0.588     1.004
#  Backreef                   0.687 0.0924 Inf     0.506     0.868
#  Forereef 10m               0.749 0.1130 Inf     0.528     0.971
#  Forereef 17m               0.940 0.1210 Inf     0.703     1.178
# $contrasts
#  contrast                    estimate    SE  df z.ratio p.value
#  Fringing - Backreef           0.1086 0.141 Inf   0.773  0.8669
#  Fringing - Forereef 10m       0.0468 0.155 Inf   0.302  0.9905
#  Fringing - Forereef 17m      -0.1446 0.161 Inf  -0.898  0.8057
#  Backreef - Forereef 10m      -0.0619 0.146 Inf  -0.424  0.9745
#  Backreef - Forereef 17m      -0.2532 0.152 Inf  -1.662  0.3442
#  Forereef 10m - Forereef 17m  -0.1913 0.166 Inf  -1.155  0.6555
```

@@

filtered_rich_stab_effects <- filter_ranges(rich_stab_emm, dss_ranges, "habitat", "richness_mean")

# V2
rich_stab_emm_2 <- emmip(rich_stab_mod_2,
                        habitat ~ richness_mean,
                        at = list(richness_mean = seq(0,10,0.01)), plotit = F, CIs = T)

filtered_rich_stab_effects_2 <- filter_ranges(rich_stab_emm_2, dss_ranges_2, "habitat", "richness_mean")

@@

# ggsave(filename = "output/figure_4a.png", figure_4a, height = 10, width = 14)

(figure_4a_2 <- 
  ggplot() +
  geom_point(data = mean_synchrony_stability,
             aes(x = richness_mean, y = stability_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_2, aes(x = richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_2, aes(x = richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "Stability\n", x = "", title = "") +
  trends_theme
         )

# ggsave(filename = "output/figure_4a_2.png", figure_4a_2, height = 10, width = 14)
```

@@

```{r mean plot fg mod}
rich_stab_mod_fg_2 <- glmmTMB(stability_mean ~ functional_richness_mean*habitat, family = Gamma(link = "log"), data = mean_synchrony_stability)
summary(rich_stab_mod_fg_2)
car::Anova(rich_stab_mod_fg_2)
#                                     Chisq Df Pr(>Chisq)    
# functional_richness_mean         194.7617  1    < 2e-16 ***
# habitat                            8.9415  3    0.03008 *  
# functional_richness_mean:habitat   0.8120  3    0.84659    
hist(residuals(rich_stab_mod_fg_2)) # looks fine
plot(residuals(rich_stab_mod_fg_2) ~ fitted(rich_stab_mod_fg_2)) # same as usual

performance::r2(rich_stab_mod_fg_2) # 0.94
emtrends(rich_stab_mod_fg_2, pairwise ~ habitat, var = "functional_richness_mean") # no differences among habitats
# $emtrends
#  habitat      functional_richness_mean.trend    SE  df asymp.LCL asymp.UCL
#  Fringing                              0.945 0.128 Inf     0.694      1.20
#  Backreef                              0.833 0.116 Inf     0.606      1.06
#  Forereef 10m                          0.858 0.146 Inf     0.571      1.14
#  Forereef 17m                          0.969 0.130 Inf     0.713      1.22
# 
# Confidence level used: 0.95 
# 
# $contrasts
#  contrast                    estimate    SE  df z.ratio p.value
#  Fringing - Backreef           0.1117 0.173 Inf   0.646  0.9170
#  Fringing - Forereef 10m       0.0871 0.194 Inf   0.448  0.9700
#  Fringing - Forereef 17m      -0.0235 0.183 Inf  -0.129  0.9992
#  Backreef - Forereef 10m      -0.0246 0.187 Inf  -0.132  0.9992
#  Backreef - Forereef 17m      -0.1353 0.175 Inf  -0.774  0.8661
#  Forereef 10m - Forereef 17m  -0.1106 0.196 Inf  -0.565  0.9426

@@

filtered_rich_stab_effects_fg <- filter_ranges(rich_stab_emm_fg, dss_ranges, "habitat", "functional_richness_mean")

## V2
rich_stab_emm_fg_2 <- emmip(rich_stab_mod_fg_2,
                        habitat ~ functional_richness_mean,
                        at = list(functional_richness_mean = seq(0,10,0.01)), plotit = F, CIs = T)

filtered_rich_stab_effects_fg_2 <- filter_ranges(rich_stab_emm_fg_2, dss_ranges_2, "habitat", "functional_richness_mean")
```

@@

#ggsave(filename = "output/figure_4b_v2.png", figure_4b, height = 10, width = 14)

## V2
(figure_4b_2 <- 
  ggplot() +
  geom_point(data = mean_synchrony_stability,
             aes(x = functional_richness_mean, y = stability_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_rich_stab_effects_fg_2, aes(x = functional_richness_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_rich_stab_effects_fg_2,
              aes(x = functional_richness_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(y = "", x = "", title = "") +
  trends_theme
         )
```

@@

```{r plot mean synchrony mod}
synch_stab_mod_2 <- glmmTMB(stability_mean ~ synchrony_mean*habitat, family = Gamma("log"), data = mean_synchrony_stability)
summary(synch_stab_mod_2)
Anova(synch_stab_mod_2)
#                          Chisq Df Pr(>Chisq)    
# synchrony_mean         28.1431  1  1.127e-07 ***
# habitat                 1.2421  3     0.7429    
# synchrony_mean:habitat  5.3778  3     0.1461    
hist(residuals(synch_stab_mod_2)) # a little chunky but looks good
plot(residuals(synch_stab_mod_2) ~ fitted(synch_stab_mod_2)) # looks good

performance::r2(synch_stab_mod_2) # 0.77
emtrends(synch_stab_mod_2, pairwise ~ habitat, var = "synchrony_mean") 
# $emtrends
#  habitat      synchrony_mean.trend    SE  df asymp.LCL asymp.UCL
#  Fringing                    -1.64 0.635 Inf     -2.89    -0.398
#  Backreef                    -3.95 1.660 Inf     -7.19    -0.700
#  Forereef 10m                -2.37 0.900 Inf     -4.13    -0.602
#  Forereef 17m                -4.49 1.190 Inf     -6.82    -2.157
# 
# Confidence level used: 0.95 
# 
# $contrasts
#  contrast                    estimate   SE  df z.ratio p.value
#  Fringing - Backreef            2.304 1.77 Inf   1.299  0.5636
#  Fringing - Forereef 10m        0.724 1.10 Inf   0.657  0.9131
#  Fringing - Forereef 17m        2.846 1.35 Inf   2.111  0.1495
#  Backreef - Forereef 10m       -1.580 1.89 Inf  -0.838  0.8363
#  Backreef - Forereef 17m        0.542 2.04 Inf   0.266  0.9934
#  Forereef 10m - Forereef 17m    2.122 1.49 Inf   1.423  0.4851
```

@@

filtered_synch_stab_effects <- filter_ranges(synch_stab_emm, dss_ranges, "habitat", "synchrony")

## V2
synch_stab_emm_2 <- emmip(synch_stab_mod_2,
                        habitat ~ synchrony_mean,
                        at = list(synchrony_mean = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_synch_stab_effects_2 <- filter_ranges(synch_stab_emm_2, dss_ranges_2, "habitat", "synchrony_mean")
```

@@

```{r figure 4c}
(figure_4c <- 
  ggplot() +
  geom_point(data = diversity_stability_synchrony,
             aes(x = synchrony, y = cover_stability, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects, aes(x = synchrony, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_stab_effects, aes(x = synchrony, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  trends_theme
         )
# ggsave(filename = "output/figure_4c.png", figure_4c, height = 10, width = 14)

## V2
(figure_4c_2 <- 
  ggplot() +
  geom_point(data = mean_synchrony_stability,
             aes(x = synchrony_mean, y = stability_mean, colour = habitat), size = 1, alpha = 0.5) + 
  geom_line(data = filtered_synch_stab_effects_2, aes(x = synchrony_mean, y = exp(yvar), colour = habitat), size = 1.5) +
  geom_ribbon(data = filtered_synch_stab_effects_2, aes(x = synchrony_mean, ymin = exp(LCL), ymax = exp(UCL), fill = habitat),
              alpha = 0.3) +
  scale_colour_manual(values = habitat_colours) +
  scale_fill_manual(values = habitat_colours) +
  labs(x = "", y = "", title = "") +
  trends_theme
         )
```

@@

### compare plot level graphs
```{r ggpubr fig4, fig.height = 8, fig.width=16}

(mean_plot_graphs <- ggarrange(figure_4a, figure_4b, figure_4c, figure_4a_2, figure_4b_2, figure_4c_2, 
                      ncol = 3, nrow = 2, 
                      common.legend = TRUE,
                      heights = c(1,1),
                      widths = c(1,1,1),
                      legend = "bottom", 
                      labels = c("a.", "b.", "c.", "d.", "e.", "f."),
                      font.label = list(size = 26, color = "black", face = "plain")))

# ggsave(filename = "output/plot_dss_graphs.png", mean_plot_graphs, height = 8, width = 16)
```
### DSS graph with mean plot
```{r ggpubr fig4, fig.height = 8, fig.width=16}
(figure_4_2 <- ggarrange(figure_4a_2, figure_4b_2, figure_4c_2, figure_4d, figure_4e, figure_4f, 
                      ncol = 3, nrow = 2, 
                      common.legend = TRUE,
                      heights = c(1,1),
                      widths = c(1,1,1),
                      legend = "bottom", 
                      labels = c("a.", "b.", "c.", "d.", "e.", "f."),
                      font.label = list(size = 26, color = "black", face = "plain")))

# ggsave(filename = "output/figure_4v3.png", figure_4_2, height = 8, width = 16)

@@
